---
title: "TASK2: PREDICTION USING UNSUPERVISED LEARNING"
author: "Yogesh S"
date: "2023-06-12"
output: html_document
---

<br>

##### **OBJECTIVE:** From given 'IRIS' Dataset predict the optimum no .of clusters.

<br>

#### **Step 1: Load the required Datasets.**
```{r}
data<-iris
head(iris)
```

<br>

#### **Step 2: Load the required libraries.**
```{r}
library(ggplot2)
library(cluster)
library(factoextra)
```

<br>

#### **Step 3: View the datasets.**
```{r}
View(iris)
str(iris)
```

<br>


#### **Step 4: Let us find the optimum number of clusters using the "ELBOW METHOD"**
```{r}
clust<-fviz_nbclust(iris [,1:4], kmeans, method = "wss")
clust
```

<br>

##### From the previous graph, we can see the bend located at "k=3". Therefore optimum no.of clusters = 3.

<br>

#### **Step 5: Let us use a clustering technique such as "K-MEANS CLUSTERING" to classify the data according to defined number of clusters"**

```{r}
set.seed(100)
Clustech<-kmeans(data[,1:4],center=3,nstart=20)
Clustech
```

<br>

#### **Step 6: Let us visualize the clustering using ggplot**
```{r}
ggplot(data,aes(Petal.Length,Petal.Width))+ geom_point(aes(col=Species),size=4)
```

<br>
